---
title: "Lab 1"
author: "Takahiro Wada"
date: "2023-02-19"
output: pdf_document
---
# Lab 1
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include = FALSE}
df = read.csv("Absenteeism_at_work.csv",sep=";",header=TRUE)
head(df)
library(dplyr)
attach(df)
```

## Question 1:
```{r}
plot(Weight, Height, main = "Scatter Plot of Weight VS Height")
```
Based on the graph we can see no correlation between weigh and height, so it is not very useful.

## Question 2:
```{r}
hist(Absenteeism.time.in.hours, main = "Histogram of Absenteeism in Hours",
     xlab = "Absenteeism in Hours")
```

Based off this graph, we see most of the employees have less than 20 Hours of absenteeism making the graph skew right.

## Question 3:
```{r}
hist(Age, breaks = 20)
```
We can determine the age demographic of our absentees. The graph is relatively distributed evenly.


## Question 4:
```{r}
library(dplyr)

HoursMonth <- df %>%
  group_by(Month.of.absence) %>%
  summarise(total_absenteeism_hours = sum(Absenteeism.time.in.hours))

barplot(HoursMonth$total_absenteeism_hours, 
        names.arg = HoursMonth$Month.of.absence, 
        xlab = "Month", 
        ylab = "Total Absenteeism Hours", 
        main = "Absenteeism Hours by Month")

```
Based on the graph, we see that March and July are the months with the largest absentee hours.


## Question 5:
```{r}
library(dplyr)

smoker <-recode_factor(df$Social.smoker, '0' = "Non-Smoker", '1' = "Smoker")
unique(smoker)
boxplot(Absenteeism.time.in.hours ~ smoker, data = df,
        xlab = "Social Smoker",
        ylab = "Absenteeism In Hours",
        main = "Box plot of Absenteeism Time by Social Smoker",
        horizontal = TRUE, col = c("blue", "red"))

```

The boxplot is skewed due to many outliers. The plot is not very useful.

## Question 6:
```{r}
library(dplyr)

drinker <-recode_factor(df$Social.drinker, '0' = "Non-Drinker", '1' = "Drinker")
unique(drinker)
boxplot(Absenteeism.time.in.hours ~ drinker, data = df,
        xlab = "Social Drinker",
        ylab = "Absenteeism In Hours",
        main = "Box plot of Absenteeism Time by Social Drinker",
        horizontal = TRUE, col = c("blue", "red"))

```
As seen as the Social Smoker's graph, the graph is also skewed with more outliers on the graph. This graph is not very useful.
